A quantitative framework for investigating the reliability of empirical network construction

### 2019-02-18 manuscript/CI_interactions.tex
starting reply 2

        Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior entails only one assumption: that the focal network has similar structural properties to those of published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network. If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

@@

  Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework. This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring based on the distribution of interactions in one ``pilot'' site. This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur. Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  \begin{figure}[h!]
    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur. Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
    \indent Interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}. Attributions for images are given in \emph{Appendix S1-A}.}
    \label{conceptual_fig}
    \begin{center}
    % \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted. \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
      \label{histograms}
      \begin{center}
      % \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
      \end{center}
      \end{figure}

@@

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    % \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}

>>>>

        Alternatively, one can develop a prior based on the properties of a set of published networks (``empirical" or ``reference Bayes"~\citet{Spiegelhalter2000}). This type of prior entails only one assumption: that the focal network has similar structural properties to those of some published networks. For example, connectance ($C=N/S^2$, where $N$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of published connectances can be used to predict the distribution of interaction probabilities in a new network that is similar to those used to construct the prior (same type of interaction, similar taxonomic resolution, habitat, etc.). If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

@@

        Note that if the focal network is substantially different from published networks, empirical Bayes will not give reasonable expectations about interaction probabilities in the focal network. [[Seems like R1 is demanding we add some more about how empirical Bayes is crap ... maybe we can say it'd give a reasonable expectation for the number of interactions but maybe not the right ones?]]

@@

  Although 374 sampling sites were not enough to obtain sufficient observations of all species pairs, we were able to reduce uncertainty about many potential interactions using a simple Bayesian framework. This framework allowed us to set confidence intervals about the probability of an unobserved interaction occurring based on the distribution of interactions in one ``pilot'' site. This gives us more reasonable estimates of interaction probabilities than assuming that no unobserved interactions actually occur. Such approaches are particularly useful when considering interactions involving species entering new ranges due to climate change or introductions. Our framework could, for example, be used to predict the probability of interaction between a galler and parasitoid at a new site on the frontier of their ranges. If the species have not been observed co-occurring at other sites, we would expect them to interact with a probability of approximately 0.1 rather than assuming that they will not interact because they have not been observed interacting elsewhere (Fig.~\ref{Salix_pdfs_cdfs}). Understanding species' interactions in novel or changing communities is important for a variety of conservation questions~\citep{Bartomeus2013,Gravel2013}, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

@@

  \begin{figure}[h!]
    \caption{Nested levels of uncertainty mean that an observed interaction matrix is unlikely to capture all of the interactions that truly occur. Some feasible interactions (black squares in True matrix) are less likely than others (grey squares; lighter grey is less likely) based on species traits. For example, lions are less likely to predate upon elephants than zebras. If our trait model is incomplete (e.g., if we neglect group hunting in lions), we might assume that elephants are too large to be lion prey and assign this interaction a probability of 0.\\
    \indent Interactions occur with different probabilities in any given sample. We show six example networks representing interactions observed over two days at three sites. Interactions which occur during fewer sampling days are less likely to be observed.\\
    \indent Not all interactions are equally detectable. For example, interactions involving cryptic species are less likely to be observed.\\
    \indent After combining these layers of uncertainty, some interactions which truly occur are very unlikely to be observed. The observed matrix (bottom) is a subsample of the true matrix where the probability of observing each interaction depends upon multiple layers of uncertainty. Note that some low-probability interactions (e.g., lion predation on zebra) are included while others (e.g., lion predation on elephants) are not. For an illustration of the way in which these levels of uncertainty combine in simulated data, and the effects of uncertainty on network structure, see \emph{Appendix S1}. Attributions for images are given in \emph{Appendix S1-A}.}
    \label{conceptual_fig}
    \begin{center}
    \includegraphics*[height=.45\textheight]{figures/conceptual_fig.eps}
    % \includegraphics*[height=.5\textheight]{Figure_1.eps}
    \end{center}
    \end{figure}

  \begin{figure}[h!]
      \caption{Despite the high replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring and those that co-occurred rarely interacted. \textbf{A)} Histogram of the number of pairs of species observed co-occurring at least once. 9794 galler-enemy pairs were never observed co-occurring (not shown).
      \textbf{B)} Histogram of the number of observed interactions between co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} For each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      % \includegraphics*[height=.6\textheight]{Figure_2.eps}
      \end{center}
      \end{figure}

@@

  \begin{figure}[h!]
    \caption{Posterior distributions for the interaction probability ($\lambda_{ij}$) for two species that have not been observed interacting ($k_{ij}=0$), based on a single site (Zillis in Graub\"{u}nden, Switzerland) from~\citet{Kopelke2017}. Posterior distributions (curves) and 95\% credible intervals (lines at top of panel) for $\lambda_{ij}$ narrow and approach zero as the number of observed co-occurrences ($n_{ij}$) increases. Diamonds indicate the maximum likelihood estimator for the mean probability of interaction.
    Dashed lines indicate threshold probabilities of 0.01, 0.05, and 0.1. The number of samples required to obtain a 95\% credible interval below each threshold increases rapidly. It takes just over 20 observed co-occurrences to be 95\% confident that $\lambda_{ij}<0.10$ but over 100 co-occurrences to be 95\% confident that $\lambda_{ij}<0.01$.}
    \label{Salix_pdfs_cdfs}
    \begin{center}
    \includegraphics*[width=.8\textwidth]{figures/GP_pdfs_increasing_N_Zillis.eps}
    % \includegraphics*[width=.8\textwidth]{Figure_4.eps}
    \end{center}
    \end{figure}
